Assimilation of conventional and satellite observations in a deep convection

### 2021-04-30 analysis/chapters/paper_ana_20181122.Rmd
Agrego dbz de CONV

---
title: "Untitled"
output:
  html_document: default
  pdf_document: default
---

@@

```{r ciclo, fig.cap="Diagram of analysis cycles between Nov 20th, 18 UTC and Nov 23rd 12 UTC plus and spin up period of 6 hours. The zoomed figure shows assimilation in one-hour centered window and new boundary conditions from GFSD every 6 hours.", out.height=400, out.width=800, fig.align="center"}
knitr::include_graphics(here("analysis", "figures", "analysis_cycle.svg"))
```

@@

files <- Sys.glob("/home/paola.corrales/datosmunin/EXP/derived_data/ppacum/*ana*mean_acum_1h.rds")

@@

}) %>% rbindlist() %>% 
  .[x %between% c(-300000, 800000) & y %between% c(-800000, 1090000)] 
}

@@

@@

```{r dbz-mean}

dates <- c("20181122100000", "20181122130000", 
           "20181122160000", "20181122190000")
files <- paste0(derived_data, "dbz/maxdbz_ana_E8_", dates, ".nc")

  meta <- unglue(basename(f), "maxdbz_ana_{exp}_{date}.nc")
  ReadNetCDF(f, vars = c(lon = "XLONG", lat = "XLAT", "max_dbz")) %>% 
    .[, ":="(exp = meta[[1]][["exp"]],
             date = ymd_hms(meta[[1]][["date"]]))] %>% 
    .[, c("x", "y") := wrf_project(lon, lat)] 
}) %>% 
  rbindlist()  %>% 
  .[, run := "RAD"]

  plot_layout(ncol = 1, guides = "collect") & 
  theme(legend.position = 'bottom')

>>>>

---
title: Assimilation of conventional and satellite observations in a deep convection
  case during RELAMPAGO using the WRF-GSI-LETFK system.
author:
- name: Paola Belén Corrales
  email: paola.corrales@cima.fcen.uba.ar
  affiliation: Some Institute of Technology
  footnote: 1
- name: Bob Security
  email: bob@example.com
  affiliation: Another University
- name: Cat Memes
  email: cat@example.com
  affiliation: Another University
  footnote: 2
- name: Derek Zoolander
  email: derek@example.com
  affiliation: Some Institute of Technology
  footnote: 2
date: "`r Sys.Date()`"
output:
  rticles::elsevier_article: 
    keep_tex: true
abstract: |
  This is the abstract.
  It consists of two paragraphs.
journal: Atmospheric Research
layout: preprint
address:
- code: Some Institute of Technology
  address: Department, Street, City, State, Zip
- code: Another University
  address: Department, Street, City, State, Zip
bibliography: mybibfile.bib
csl: elsevier-harvard.csl
footnote:
- code: 1
  text: Corresponding Author
- code: 2
  text: Equal contribution
---

@@

```{r ciclo, fig.cap="Diagram of analysis cycles between Nov 20th, 18 UTC and Nov 23rd 12 UTC plus and spin up period of 6 hours. The zoomed figure shows assimilation in one-hour centered window and new boundary conditions from GFSD every 6 hours."}
knitr::include_graphics(here("analysis", "figures", "analysis_cycle.pdf"))
```

@@

files <- Sys.glob("/home/paola.corrales/datosmunin/EXP/derived_data/ppacum/E[2568]_ana*mean_acum_1h.rds")

@@

}) %>% rbindlist() %>% 
  .[x %between% c(-300000, 800000) & y %between% c(-800000, 1090000)]

@@

```{r dbz-mean, fig.cap="Figure 14. Observed maximum reflectivity in the column (upper row) and ensemble mean maximum reflectivity for CONV and RAD at different times (bottom two rows)."}
proj_radar <- "+proj=tmerc +lon_0=-61.5 +lat_0=-32 +k_0=1 +ellps=WGS84"

dates <- c("20181122100000", "20181122130000", 
           "20181122160000", "20181122190000")
files <- Sys.glob(paste0(derived_data, "dbz/maxdbz_ana_E[28]_", dates, ".nc"))

  meta <- unglue(basename(f), "maxdbz_ana_{exp}_{date}.nc")
  ReadNetCDF(f, vars = c(lon = "XLONG", lat = "XLAT", "max_dbz")) %>% 
    .[, ":="(exp = meta[[1]][["exp"]],
             date = ymd_hms(meta[[1]][["date"]]))] %>% 
    .[, c("x", "y") := wrf_project(lon, lat)] 
}) %>% 
  rbindlist()  %>% 
  .[, run := fifelse(exp == "E8", "RAD", "CONV")]

  plot_layout(ncol = 1, heights = c(1, 2), guides = "collect") & 
  theme(legend.position = 'bottom')

@@
